### 2021-03-17 Reports/JOURNAL - Confidence Regions/Chapters/Results.tex
update

\subsection{Descriptive analysis of empirical confidence regions}

The regions used as a reference in this work are obtained through true random sequences, where we extract the empirical distribution of white noises in the Entropy-Complexity plane.
In Fig.~\ref{fig:HC-PCA} we show the results obtained for $T = 50000$ in the scenarios of $D = 3$ and $D = 6$ in the new space defined by the PCA, together with the quantiles of $\SI{90}{\percent}$, $\SI{95}{\percent}$, $\SI{99}{\percent}$, and $\SI{99.9}{\percent}$.
We also show the projection of the $H \times C$ plane limits in this new representation space, as well as identifying the median of each data set, the latter being represented as the red dots present in the graphs.

\begin{figure}
	\centering
	\includegraphics[width=.45\linewidth]{Figures/HC-PCA-Trozos-D3N50k.png}
	\includegraphics[width=.45\linewidth]{Figures/HC-PCA-Trozos-D6N50k.png}
	\caption{Representation of truly random sequences with length $T = 50.000$ in the PCA space for $D = 3$ and $D = 6$, and the quantiles of $\SI{90}{\percent}$, $\SI{95}{\percent}$, $\SI{99}{\percent}$, and $\SI{99.9}{\percent}$.}
	\label{fig:HC-PCA}
\end{figure}

As we can see in Fig.~\ref{fig:PCA-Hist} in the new representation space produced by the PCA, the data are not evenly distributed among the axes of the first main component, maintaining the character presented in the $H \times C$ plane, since such points tend to be concentrated close to the point $(1, 0)$.

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{PCA-hist-50k}
    \caption{Histogram of the PCA first component }
    \label{fig:PCA-Hist}
\end{figure}

\subsection{Testing White Noise in the confidence regions}

To analyze the efficiency of the confidence region calculated, we tested its applicability on a set of true random data generated physically not used by the algorithm during its construction. 
The results can be seen in Fig.~\ref{fig:RNG}.

For small series, $T = 1000$, and $D = 3$ we managed to maintain exactly $\SI{99}{\percent}$ of the data in the confidence region of the same value, and as the dimension increased reach $\SI{96}{\percent}$ of the points.
On the other hand, there was a very large loss of points located in the region with $\SI{95}{\percent}$ confidence as the dimension increased.
A reasonable explanation for this event is given in the choice of the parameter itself.
It is known by definition that $D! << N$, which does not happen for such a sample size, thus presenting many missing patterns that lead to an unrepresentative probability distribution.
For larger series, $T = 50000$, although we observed a small drop in the percentage of data present in the region with $\SI{99}{\percent}$ confidence, there was a significant increase in points in the region with $\SI{95}{\percent}$ confidence, showing between $\SI{90}{\percent}$ and $\SI{88}{\percent}$ of the points when we vary the embedding dimension.

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{Figures/RNG-1000.pdf}
    \includegraphics[width=\linewidth]{Figures/RNG-50000.pdf}
    \caption{Results of the analysis behavior of true random noises in the regions of confidence built.}
    \label{fig:RNG}
\end{figure}

\subsection{Analyzing Robustness to Correlation Structures}
% k=0 white
% k=1 pink
% k=2 brown
% T = 1000, T = 5 10^5
% D= 3, D = 6

Fig.~\ref{fig:AllSystems} shows the behavior of random time series with different levels of correlation (by means of the $f^{-k}$ model) in the $(h,c)$ plane.
Knowing that such plane can discriminate between different system dynamics, several studies in the literature have used this approach in the investigation of methods of identification and characterization of randomness.
Although this same strategy can be used to characterize different levels of correlation structures, in our case, we want to analyze the impact of injecting such dynamics into noise under the aspect of confidence regions.

For carrying out the experiment, we used an ''emblematic'' time series as a basis.
This series consists of the sample corresponding to the median of the $(h,c)$ points used to build the confidence regions, thus expressing a representative sample of the dataset.
Fig.~\ref{fig:correlation}a. illustrates, respectively, the effect of a white noise time series when adding correlation structures related to the $f^{-k}$ series for $k \in \{0, 1, 2, 3 \}$.
As we can observe in the plane as the correlation between the observations increases, that is, $k > 0$, the randomness decreases and the entropy presented decreases, informing the loss of its stochastic characteristic.

Fig.~\ref{fig:correlation}b. illustrates the degree of limit correlation structure that can be added in white noise to eliminate it from the regions of confidence, where the red dot represents the original "emblematic" series.
When we have $k = 0$, the features of the sequence have a small variation, corroborating the premise that series of noise $f^{-k} = 0$ have a minimum correlation measure, not significantly changing the dynamics of the system.

\begin{figure}
    \centering
	\includegraphics[width=.48\linewidth]{Figures/Correlation-Analysis-dotted.pdf}
    \includegraphics[width=.48\linewidth]{Figures/Correlation-Analysis-point.pdf}
    \caption{Correlation Structure Analysis}
    \label{fig:correlation}
\end{figure}

@@

In this section, we evaluate the quality of the confidence regions preceded by HC-PCA with sequences of previously analyze generators in the literature with the Entropy-Complexity plane.
For this, we produced $100$ sequences of length $T = \num[scientific-notation=true]{5 e4}$ for each generator present in table~\ref{Tab:Literature} and calculated the respective p-values for each configuration of $D = \{3, 4, 5, 6\}$.
The results obtained can be seen in table~\ref{Tab:LiteratureComparations}, where we categorize the sets of sequences among those that did not reject (NR) the null hypothesis presented in the HC-PCA test and those that rejected (R).

Performing a comparative analysis of the results produced by tables~\ref{Tab:Literature} and~\ref{Tab:LiteratureComparations}, we can see that the proposed methodology of confidence regions can capture the random dynamics of the sequences produced by most of the analyzed generators well, although in our experiments we consider only short sequences.

However, two results deserve special attention: the sequences produced by the generators fBm and Combo RNG.
The first one, although it was not rejected by the analysis of~\cite{olivares2012contrasting}, presented low p-values, due to the characteristic point in the $H \times C$ plane where its sequences belong.
For the case analyzed in~\cite{olivares2012contrasting} with $D = 6$, we verified that the produced sequences present an average of $H = 0.997$, therefore they do not belong to the empirical $\SI{95}{\percent}$ confidence region produced by HC-PCA.
Analyzing the results produced by the Combo RNG, we can verify that only for $D = 3$ the proposed method can characterize the sequences produced as random.
This is due to the fact that by presenting higher dimension values, we were able to analyze a greater number of ordinal patterns, which may not be presented in their entirety in short sequences.

>>>>

\subsection{Empirical confidence regions}

Tables~\ref{Tab:Points1k} and~\ref{Tab:Points50k} list the coordinates in the $H\times C$ plane
of the emblematic point $\bm P'$ and of the four points $\bm P_1,\bm P_2,\bm P_3,\bm P_4$ that define the confidence regions at \SI{90}{\percent}, \SI{95}{\percent}, \SI{99}{\percent}, and \SI{99.9}{\percent}, 
for $D=3,4,5,6$ and $N=1000,50000$, .
The points are presented counterclockwise, starting with the one with the largest complexity.

\begin{comment}
\begin{table}[hbt]
\caption{Coordinates in the $H\times C$ plane of the emblematic series and the points that define the confidence regions at \SI{90}{\percent}, \SI{95}{\percent}, \SI{99}{\percent}, and \SI{99.9}{\percent} for $D=3,4,5,6$ and $N=1000,50000$}\label{Tab:Points}
\centering
\begin{tabular}{rcllllllll}
\toprule
& & \multicolumn{8}{c}{$N$}\\ \cmidrule(lr){3-10}
& & \multicolumn{4}{c}{$1000$} & \multicolumn{4}{c}{$50000$}\\ \cmidrule(lr){3-6} \cmidrule(lr){7-10}
$D$ & Point & \SI{90}{\percent} & \SI{95}{\percent} & \SI{99}{\percent} & \SI{99.9}{\percent} & \SI{90}{\percent} & \SI{95}{\percent} & \SI{99}{\percent} & \SI{99.9}{\percent}\\ \cmidrule(lr){3-3} \cmidrule(lr){4-4} \cmidrule(lr){5-5} \cmidrule(lr){6-6} \cmidrule(lr){7-7} \cmidrule(lr){8-8} \cmidrule(lr){9-9} \cmidrule(lr){10-10}
$3$ & $\bm P'$ & \multicolumn{4}{c}{$h',c'$} & \multicolumn{4}{c}{$h',c'$}\\
& $\bm P_1$ & $(0.9973334, 0.0025601)$ & $(0.9967311, 0.0031343)$ & $(0.9953009, 0.0045054)$ & $(0.9931825, 0.0065387)$ & $(0.9999489, \num[scientific-notation=true]{5.06e-05})$ & $(0.9999384, \num[scientific-notation=true]{6.11e-05})$ & $(0.9999079, \num[scientific-notation=true]{9.11e-05})$ & $(0.9998625, 0.0001361)$\\
& $\bm P_2$ & $(0.9974047, 0.0026304)$ & $(0.9968219, 0.0032238)$ & $(0.9954349, 0.0046375)$ & $(0.9933704, 0.006724)$ & $(0.9999487, \num[scientific-notation=true]{5.04e-05})$ & $(0.9999382, \num[scientific-notation=true]{6.09e-05})$ & $(0.9999077, \num[scientific-notation=true]{9.09e-05})$ & $(0.9998622, 0.0001358)$\\
& $\bm P_3$ & $(0.9999497, 0)$ & $(0.9999398, 0)$ & $(0.9999203, 0)$ & $(0.9998925, 0)$ & $(0.9999998, \num[scientific-notation=true]{4e-07})$ & $(0.9999994, \num[scientific-notation=true]{9e-07})$ & $(0.9999982, \num[scientific-notation=true]{2e-06})$ & $(0.9999973, \num[scientific-notation=true]{3e-06})$\\
& $\bm P_4$ & $(1, \num[scientific-notation=true]{5.17e-05})$ & $(1, \num[scientific-notation=true]{6.12e-05})$ & $(1, \num[scientific-notation=true]{8.45e-05})$ & $(1, 0.0001104)$ & $(0.9999996, \num[scientific-notation=true]{2e-07})$ & $(0.9999991, \num[scientific-notation=true]{7e-07})$ & $(0.999998, \num[scientific-notation=true]{1.8e-06})$ & $(0.999997, \num[scientific-notation=true]{2.7e-06})$\\ \midrule
$4$ & $\bm P'$ & \multicolumn{4}{c}{$h',c'$} & \multicolumn{4}{c}{$h',c'$}\\
& $\bm P_1$ & $(0.994364, 0.0081246)$ & $(0.9937138, 0.0089796)$ & $(0.9922575, 0.0108947)$ & $(0.9902578, 0.0135243)$ & $(0.9999684, \num[scientific-notation=true]{3.98e-05})$ & $(0.9999725, \num[scientific-notation=true]{3.44e-05})$ & $(0.9999783, \num[scientific-notation=true]{2.68e-05})$ & $(0.9999833, \num[scientific-notation=true]{2.02e-05})$ \\
& $\bm P_2$ & $(0.9939234, 0.0075452)$ & $(0.9932534, 0.0083741)$ & $(0.9917308, 0.0102022)$ & $(0.9897312, 0.0128318)$ & $(0.9999696, \num[scientific-notation=true]{4.13e-05})$ & $(0.9999737, \num[scientific-notation=true]{3.6e-05})$ & $(0.9999795, \num[scientific-notation=true]{2.83e-05})$ & $(0.9999845, \num[scientific-notation=true]{2.18e-05})$ \\
& $\bm P_3$ & $(0.9994791, 0.0013982)$ & $(0.9991609, 0.0018166)$ & $(0.9987924, 0.0023012)$ & $(0.9985727, 0.0025901)$ & $(0.9998075, 0.0002508)$ & $(0.9998506, 0.0001942)$ & $(0.9998756, 0.0001615)$ & $(0.9998889, 0.000144)$ \\
& $\bm P_4$ & $(0.9990385, 0.0008188)$ & $(0.9987005, 0.0012111)$ & $(0.9982658, 0.0016087)$ & $(0.9980461, 0.0018976)$ & $(0.9998087, 0.0002524)$ & $(0.9998518, 0.0001958)$ & $(0.9998768, 0.000163)$ & $(0.9998901, 0.0001456)$ \\ \midrule
$5$ & $\bm P'$ & \multicolumn{4}{c}{$h',c'$} & \multicolumn{4}{c}{$h',c'$}\\
& $\bm P_1$ & $(0.9811818, 0.0321294)$ & $(0.9801289, 0.0340045)$ & $(0.977917, 0.0377295)$ & $(0.9753326, 0.0425299)$ & $(0.9998172, 0.0003232)$ & $(0.9998259, 0.0003075)$ & $(0.9998428, 0.0002774)$ & $(0.9998573, 0.0002517)$ \\
& $\bm P_2$ & $(0.9827429, 0.0350291)$ & $(0.9817117, 0.0369446)$ & $(0.9796031, 0.0408613)$ & $(0.9770187, 0.0456617)$ & $(0.9998194, 0.0003273)$ & $(0.9998282, 0.0003116)$ & $(0.999845, 0.0002814)$ & $(0.9998593, 0.0002553)$ \\
& $\bm P_3$ & $(0.9919707, 0.0120896)$ & $(0.9909376, 0.0139279)$ & $(0.9898161, 0.0156277)$ & $(0.9892599, 0.0166608)$ & $(0.9994812, 0.0009246)$ & $(0.9996371, 0.0006455)$ & $(0.9996703, 0.0005862)$ & $(0.9996884, 0.000554)$ \\
& $\bm P_4$ & $(0.9935319, 0.0149893)$ & $(0.9925204, 0.016868)$ & $(0.9915021, 0.0187595)$ & $(0.9909459, 0.0197926)$ & $(0.9994834, 0.0009286)$ & $(0.9996394, 0.0006495)$ & $(0.9996725, 0.0005901)$ & $(0.9996904, 0.0005576)$ \\ \midrule
$6$ & $\bm P'$ & \multicolumn{4}{c}{$h',c'$} & \multicolumn{4}{c}{$h',c'$}\\
& $\bm P_1$ & $(0.9121895, 0.2201993)$ & $(0.9105951, 0.2239294)$ & $(0.9105951, 0.2239294)$ & $(0.9077672, 0.2305874)$ & $(0.9990169, 0.002336)$ & $(0.9990368, 0.002288)$ & $(0.9990736, 0.0021997)$ & $(0.9991069, 0.0021197)$ \\
& $\bm P_2$ & $(0.9146048, 0.2260776)$ & $(0.9130413, 0.2298829)$ & $(0.9130413, 0.2298829)$ & $(0.9102595, 0.2366531)$ & $(0.9990249, 0.0023554)$ & $(0.9990449, 0.0023074)$ & $(0.9990817, 0.0022191)$ & $(0.999115, 0.0021392)$ \\
& $\bm P_3$ & $(0.9443868, 0.1418373)$ & $(0.9419202, 0.1476904)$ & $(0.9396577, 0.1531967)$ & $(0.9383611, 0.1561279)$ & $(0.9978983, 0.0050219)$ & $(0.998714, 0.0030633)$ & $(0.998765, 0.0029407)$ & $(0.9987884, 0.0028845)$ \\
& $\bm P_4$ & $(0.9468021, 0.1477156)$ & $(0.9443663, 0.1536439)$ & $(0.9421039, 0.1591502)$ & $(0.9408534, 0.1621937)$ & $(0.9979064, 0.0050413)$ & $(0.998722, 0.0030827)$ & $(0.9987731, 0.0029601)$ & $(0.9987965, 0.0029039)$ \\ \bottomrule
\end{tabular}
\end{table}
\end{comment}

\begin{table}[hbt]
	\caption{Coordinates in the $H\times C$ plane of the emblematic series and the points that define the confidence regions at \SI{90}{\percent}, \SI{95}{\percent}, \SI{99}{\percent}, and \SI{99.9}{\percent} for $D=3,4,5,6$ and $N=1000$}\label{Tab:Points1k}
	\centering
	\begin{tabular}{rccccc}
		\toprule
		%& & \multicolumn{4}{c}{$N$}\\ 
		%\cmidrule(lr){3-6}
		& & \multicolumn{4}{c}{$N = 1000$}\\ 
		\cmidrule(lr){3-6} 
		$D$ & Point & \SI{90}{\percent} & \SI{95}{\percent} & \SI{99}{\percent} & \SI{99.9}{\percent}\\ 
		\cmidrule(lr){3-3} 
		\cmidrule(lr){4-4} 
		\cmidrule(lr){5-5} 
		\cmidrule(lr){6-6} 
		$3$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9992089,0.0007800)$}\\
		& $\bm P_1$ & $(0.9973334, 0.0025601)$ & $(0.9967311, 0.0031343)$ & $(0.9953009, 0.0045054)$ & $(0.9931825, 0.0065387)$\\
		& $\bm P_2$ & $(0.9974047, 0.0026304)$ & $(0.9968219, 0.0032238)$ & $(0.9954349, 0.0046375)$ & $(0.9933704, 0.006724)$\\
		& $\bm P_3$ & $(0.9999497, 0)$ & $(0.9999398, 0)$ & $(0.9999203, 0)$ & $(0.9998925, 0)$\\
		& $\bm P_4$ & $(1, \num[scientific-notation=true]{5.17e-05})$ & $(1, \num[scientific-notation=true]{6.12e-05})$ & $(1, \num[scientific-notation=true]{8.45e-05})$ & $(1, 0.0001104)$\\ 
		\midrule
		$4$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9967032, 0.0043297)$} \\
		& $\bm P_1$ & $(0.994364, 0.0081246)$ & $(0.9937138, 0.0089796)$ & $(0.,9922575 0.0108947)$ & $(0.9902578, 0.0135243)$\\
		& $\bm P_2$ & $(0.9939234, 0.0075452)$ & $(0.9932534, 0.0083741)$ & $(0.9917308, 0.0102022)$ & $(0.9897312, 0.0128318)$\\
		& $\bm P_3$ & $(0.9994791, 0.0013982)$ & $(0.9991609, 0.0018166)$ & $(0.9987924, 0.0023012)$ & $(0.9985727, 0.0025901)$\\
		& $\bm P_4$ & $(0.9990385, 0.0008188)$ & $(0.9987005, 0.0012111)$ & $(0.9982658, 0.0016087)$ & $(0.9980461, 0.0018976)$\\ 
		\midrule
		$5$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9864873, 0.0245632)$}\\
		& $\bm P_1$ & $(0.9811818, 0.0321294)$ & $(0.9801289, 0.0340045)$ & $(0.977917, 0.0377295)$ & $(0.9753326, 0.0425299)$\\
		& $\bm P_2$ & $(0.9827429, 0.0350291)$ & $(0.9817117, 0.0369446)$ & $(0.9796031, 0.0408613)$ & $(0.9770187, 0.0456617)$\\
		& $\bm P_3$ & $(0.9919707, 0.0120896)$ & $(0.9909376, 0.0139279)$ & $(0.9898161, 0.0156277)$ & $(0.9892599, 0.0166608)$\\
		& $\bm P_4$ & $(0.9935319, 0.0149893)$ & $(0.9925204, 0.016868)$ & $(0.9915021, 0.0187595)$ & $(0.9909459, 0.0197926)$\\ 
		\midrule
		$6$ & $\bm P'$ & \multicolumn{4}{c}{$(0,9296429, 0.1841438)$}\\
		& $\bm P_1$ & $(0.9121895, 0.2201993)$ & $(0.9105951, 0.2239294)$ & $(0.9105951, 0.2239294)$ & $(0.9077672, 0.2305874)$\\
		& $\bm P_2$ & $(0.9146048, 0.2260776)$ & $(0.9130413, 0.2298829)$ & $(0.9130413, 0.2298829)$ & $(0.9102595, 0.2366531)$\\
		& $\bm P_3$ & $(0.9443868, 0.1418373)$ & $(0.9419202, 0.1476904)$ & $(0.9396577, 0.1531967)$ & $(0.9383611, 0.1561279)$\\
		& $\bm P_4$ & $(0.9468021, 0.1477156)$ & $(0.9443663, 0.1536439)$ & $(0.9421039, 0.1591502)$ & $(0.9408534, 0.1621937)$\\ 
		\bottomrule
	\end{tabular}
\end{table}

\begin{table}[hbt]
	\caption{Coordinates in the $H\times C$ plane of the emblematic series and the points that define the confidence regions at \SI{90}{\percent}, \SI{95}{\percent}, \SI{99}{\percent}, and \SI{99.9}{\percent} for $D=3,4,5,6$ and $N=50000$}\label{Tab:Points50k}
	\centering
	\begin{tabular}{rccccc}
		\toprule
		%& & \multicolumn{4}{c}{$N$}\\ 
		%\cmidrule(lr){3-6}
		& & \multicolumn{4}{c}{$N = 50000$}\\ 
		\cmidrule(lr){3-6} 
		$D$ & Point & \SI{90}{\percent} & \SI{95}{\percent} & \SI{99}{\percent} & \SI{99.9}{\percent}\\ 
		\cmidrule(lr){3-3} 
		\cmidrule(lr){4-4} 
		\cmidrule(lr){5-5} 
		\cmidrule(lr){6-6} 
		$3$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9999853, \num[scientific-notation=true]{1.45e-05})$}\\
		& $\bm P_1$ & $(0.9999489, \num[scientific-notation=true]{5.06e-05})$ & $(0.9999384, \num[scientific-notation=true]{6.11e-05})$ & $(0.9999079, \num[scientific-notation=true]{9.11e-05})$ & $(0.9998625, 0.0001361)$\\
		& $\bm P_2$ & $(0.9999487, \num[scientific-notation=true]{5.04e-05})$ & $(0.9999382, \num[scientific-notation=true]{6.09e-05})$ & $(0.9999077, \num[scientific-notation=true]{9.09e-05})$ & $(0.9998622, 0.0001358)$\\
		& $\bm P_3$ & $(0.9999998, \num[scientific-notation=true]{4e-07})$ & $(0.9999994, \num[scientific-notation=true]{9e-07})$ & $(0.9999982, \num[scientific-notation=true]{2e-06})$ & $(0.9999973, \num[scientific-notation=true]{3e-06})$\\
		& $\bm P_4$ & $(0.9999996, \num[scientific-notation=true]{2e-07})$ & $(0.9999991, \num[scientific-notation=true]{7e-07})$ & $(0.999998, \num[scientific-notation=true]{1.8e-06})$ & $(0.999997, \num[scientific-notation=true]{2.7e-06})$\\ \midrule
		$4$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9999394, \num[scientific-notation=true]{7.94e-05})$}\\
		& $\bm P_1$ & $(0.9999684, \num[scientific-notation=true]{3.98e-05})$ & $(0.9999725, \num[scientific-notation=true]{3.44e-05})$ & $(0.9999783, \num[scientific-notation=true]{2.68e-05})$ & $(0.9999833, \num[scientific-notation=true]{2.02e-05})$ \\
		& $\bm P_2$ & $(0.9999696, \num[scientific-notation=true]{4.13e-05})$ & $(0.9999737, \num[scientific-notation=true]{3.6e-05})$ & $(0.9999795, \num[scientific-notation=true]{2.83e-05})$ & $(0.9999845, \num[scientific-notation=true]{2.18e-05})$ \\
		& $\bm P_3$ & $(0.9998075, 0.0002508)$ & $(0.9998506, 0.0001942)$ & $(0.9998756, 0.0001615)$ & $(0.9998889, 0.000144)$ \\
		& $\bm P_4$ & $(0.9998087, 0.0002524)$ & $(0.9998518, 0.0001958)$ & $(0.9998768, 0.000163)$ & $(0.9998901, 0.0001456)$ \\ \midrule
		$5$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9997616, 0.0004264)$}\\
		& $\bm P_1$ & $(0.9998172, 0.0003232)$ & $(0.9998259, 0.0003075)$ & $(0.9998428, 0.0002774)$ & $(0.9998573, 0.0002517)$ \\
		& $\bm P_2$ & $(0.9998194, 0.0003273)$ & $(0.9998282, 0.0003116)$ & $(0.999845, 0.0002814)$ & $(0.9998593, 0.0002553)$ \\
		& $\bm P_3$ & $(0.9994812, 0.0009246)$ & $(0.9996371, 0.0006455)$ & $(0.9996703, 0.0005862)$ & $(0.9996884, 0.000554)$ \\
		& $\bm P_4$ & $(0.9994834, 0.0009286)$ & $(0.9996394, 0.0006495)$ & $(0.9996725, 0.0005901)$ & $(0.9996904, 0.0005576)$ \\ \midrule
		$6$ & $\bm P'$ & \multicolumn{4}{c}{$(0.9989108, 0.0026093)$}\\
		& $\bm P_1$ & $(0.9990169, 0.002336)$ & $(0.9990368, 0.002288)$ & $(0.9990736, 0.0021997)$ & $(0.9991069, 0.0021197)$ \\
		& $\bm P_2$ & $(0.9990249, 0.0023554)$ & $(0.9990449, 0.0023074)$ & $(0.9990817, 0.0022191)$ & $(0.999115, 0.0021392)$ \\
		& $\bm P_3$ & $(0.9978983, 0.0050219)$ & $(0.998714, 0.0030633)$ & $(0.998765, 0.0029407)$ & $(0.9987884, 0.0028845)$ \\
		& $\bm P_4$ & $(0.9979064, 0.0050413)$ & $(0.998722, 0.0030827)$ & $(0.9987731, 0.0029601)$ & $(0.9987965, 0.0029039)$ \\ \bottomrule
	\end{tabular}
\end{table}

Fig.~\ref{fig:HC-PCA} shows the results for $T = 50000$ and $D = 3,6$ in the new principal components space, along with the quantiles of order $\SI{90}{\percent}$, $\SI{95}{\percent}$, $\SI{99}{\percent}$, and $\SI{99.9}{\percent}$.
We also show the projection of the $H \times C$ plane boundaries in this space, as well the median of each data set, the latter being represented as red dots.

\begin{figure}[hbt]
	\centering
	\subfloat[Points in the Principal Components plane for for $D=3$]{\includegraphics[width=.49\linewidth]{Figures/HC-PCA-Trozos-D3N50k}}
	\subfloat[Points in the Principal Components plane for for $D=6$]{\includegraphics[width=.49\linewidth]{Figures/HC-PCA-Trozos-D6N50k}}
	\caption{Representation of true random white noise sequences of length $T = 50000$ in the PCA space for $D = 3$ and $D = 6$, and the quantiles of $\SI{90}{\percent}$, $\SI{95}{\percent}$, $\SI{99}{\percent}$, and $\SI{99.9}{\percent}$.}
	\label{fig:HC-PCA}
\end{figure}

The confidence regions exceed the $H \times C$ boundaries, but this issue does not compromise the test's size since no points can be observed outside such boundaries.

Fig.~\ref{fig:HC-PCA} also shows that the data are not evenly distributed among the axes of the first principal component.
They tend to concentrate close to the point that corresponds to $(1,0)$ in the $H\times C$ plane.
As we use order statistics to define the confidence regions, this issue is also of little relevance for our results.
Moreover, Fig.~\ref{fig:PCA-Hist} shows that such asymmetry diminishes when the embedding dimension $D$ increases.

\begin{figure}[hbt]
	\centering
	\includegraphics[width=\linewidth]{PCA-hist-50k}
	\caption{Histograms of the first principal component for $D=3,4,5,6$}
	\label{fig:PCA-Hist}
\end{figure}

\subsection{Test Size}

We assessed the size of the test by contrasting $100$ new TWNRS for each situation of $D=3,4,5,6$ and of $\alpha=0.01,0.05$.
Table~\ref{tab:result1} and Fig.~\ref{fig:RNG} 
show the results.

On the one hand, long series ($T=50000$) present a good size for every embedding dimension.
On the other hand, short series ($T=1000$) exhibit only one situation with a noticeable divergence between the expected and the observed size: the test rejects \SI{13}{\percent} of the $100$ series when $D=6$. 
In contrast, we expected \SI{1}{\percent} of rejection.
This might be because, in this case, the condition $D!\ll T$ is not respected.
Notice that the wrongly rejected TWNRS are all close to the point $(1,0)$.

%
%For large series, $T = 50000$, the closest although we observed a small drop in the percentage of data present in the region with $\SI{99}{\percent}$ confidence, there was a significant increase in points in the region with $\SI{95}{\percent}$ confidence, showing between $\SI{90}{\percent}$ and $\SI{88}{\percent}$ of the points when we vary the embedding dimension.
%
%For short series, $T = 1000$, and $D = 3$ 
%the conficence region at $\SI{99}{\percent}$ contains exactly $\SI{99}{\percent}$.
%
%On the other hand, there was a very large loss of points located in the region with $\SI{95}{\percent}$ confidence as the dimension increased.
%A reasonable explanation for this event is given in the choice of the parameter itself.
%It is known by definition that $D! \ll N$, which does not happen for such a sample size, thus presenting many missing patterns that lead to an unrepresentative probability distribution.

\begin{table}[hbt]
	\centering
	\caption{Empirical sizes of the test}
	\label{tab:result1}
	\begin{tabular}{*{3}rr}
		\toprule
		\multicolumn{1}{c}{$N$} & \multicolumn{1}{c}{$D$} & \multicolumn{1}{c}{\SI{95}{\percent}} & \multicolumn{1}{c}{\SI{99}{\percent}}\\
		%& $p$-value\\
		\cmidrule(lr){1-1}
		\cmidrule(lr){2-2}
		\cmidrule(lr){3-3}
		\cmidrule(lr){4-4}
		1000 & 3 & $0.98$ & $1.00$\\
		& 4 & $0.98$ & $0.96$\\
		& 5 & $1.00$ & $0.94$\\
		& 6 & $0.97$ & $0.87$\\
		\cmidrule(lr){1-4} 
		50000 & 3 & $0.97$ & $0.96$\\
		%& $0.47856$\\
		& 4 & $0.94$ & $0.95$\\
		%& $0.47555$\\ 
		& 5 & $0.97$ & $0.96$\\ 
		%& $0.48512$\\ 
		& 6 & $0.98$ & $0.99$\\ 
		%& $0.48058$\\
		\bottomrule
	\end{tabular}
\end{table}

\begin{figure}[hbt]
	\centering
	\includegraphics[width=\linewidth]{Figures/RNG-1000.pdf}
	\includegraphics[width=\linewidth]{Figures/RNG-50000.pdf}
	\caption{New $100$ TRWNS and regions of confidence.}
	\label{fig:RNG}
\end{figure}

We may then conclude that the test has good empirical size, provided $D!\ll T$, a condition that does not hold for $D=6$ and $T=1000$.

\subsection{Test Power}

We assessed the power of the test by contrasting time series with different correlation structure (under the $f^{-k}$ model) in the $H \times C$ plane.
Several studies in the literature have used this approach for identifying and characterizing randomness.

Our study's basis is the emblematic time series for each length $T$ and dimension embedding $D$.
Recall that the emblematic time was chosen as the most representative of the data set.
We use these series, transform them into $f^{-k}$ correlated noise, and verify the new point's location in the $H\times C$ plane.

%Fig.~\ref{fig:CorrNoisea} illustrates the effect of a white noise time series when adding correlation structures related to the $f^{-k}$ series for $k \in \{0, 1, 2, 3 \}$.
As we can observe in the plane, as the correlation between the observations increases, that is, $k > 0$, the randomness decreases, and the entropy presented decreases, informing the loss of its stochastic characteristic.

Fig.~\ref{fig:CorrNoisea} shows the overall effect of transforming the emblematic time series into $f^{-k}$ correlated noise, with $k=1/2,1,3/2,2,5/2,3$.
At this scale, the emblematic time series $k=0$ and the one with $k=1/2$ appear overlapped.
As the correlation increases with $k$, the randomness decreases, causing a drop in the entropy; the series become progressively more predictable.

Fig.~\ref{fig:CorrNoiseb} is a zoom close to the $(1,0)$ point, along with the confidence regions for the white noise.
We see that $ k = 0 $ and $ k = 0.1 $ are inside the $\SI{95}{\percent}$ confidence region, and $ k = 0.2 $ is inside the $\SI{99}{\percent}$ box.
Notice that the time series with $k=3/10$ is outside the confidence regions and does not pass the randomness test.
The same holds for all $k>3/10$.

\begin{figure}
	\centering
	\subfloat[Points in the $H\times C$ plane of the emblematic white noise  ($k=0$) and its transformations to become $f^{-k}$ correlated noise with $k=1/2,1,3/2,2,5/2,3$.\label{fig:CorrNoisea}]{
		\includegraphics[width=.48\linewidth]{Figures/Correlation-Analysis-dotted.pdf}}
	\subfloat[Points of the emblematic white noise ($k=0$), and its $f^{-k}$ correlated noise versions, with $k=1/10, 1/5,3/10$ along with the confidence regions for white noise.\label{fig:CorrNoiseb}]{
		\includegraphics[width=.48\linewidth]{Figures/Correlation-Analysis-point.pdf}}
	\caption{Analysis of the test power with correlated $f^{-k}$ noise.}
	\label{fig:correlation}
\end{figure}

@@

In this section, we compare the performance of our test with that of 
previous analyses that employ the Entropy-Complexity plane.
To this aim, we produced $100$ sequences of length $T = \num[scientific-notation=true]{5 e4}$ for each generator and computed the $p$-value for each $D = \{3, 4, 5, 6\}$.
Previous results are shown in Table~\ref{Tab:Literature}, and ours are in Table~\ref{Tab:LiteratureComparations}.
We grouped our results in those that rejected (R) the null hypothesis and those that did not reject it (NR).
